On the presentation of orthogonal groups over polynomial rings

### 2019-01-16 dl-paper.tex
Couple more of lemmas added

The aim of this section is to briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups. We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).

@@

\subsection{Isogenous forms of the orthogonal group}
\subsection{Grothendieck--Witt groups}
\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}
For a commutative ring $A$ with an ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$.
Consider the following commutative square of canonical maps.
\[ \xymatrix{
    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]_\mu & \St(\Phi, R)
   } \]
Then there exists an arrow $\mu$ which makes the diagram commute.   
\end{lemma} 
\begin{proof}
 Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
 Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.

@@

\begin{lemma}
 Let $F$ be a field of characteristic $\neq 2$. Then for $\ell \geq 7$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
\end{lemma}
\begin{proof}
 We have defined $\K_3(\rD_\ell, R)$ as 
\end{proof}

@@

\include{rehmann}

>>>>

The aim of this section is to briefly remind the reader definitions of relative Steinberg groups and their basic properties. We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).

@@

%\subsection{Isogenous forms of the orthogonal group}
\subsection{Hermitian K-theory and higher Grothendieck--Witt groups}
In this section we collect some facts pertaining to Hermitian K-theory that will be of relevance to us. We refer the reader to~\cite[\S~2]{AF17} or~\cite[\S~2]{FRS12} for a more detailed introduction.

First of all, recall that in~\cite{Ka80} M.~Karoubi defines higher Grothendieck--Witt groups via Quillen's plus-construction:

Schlichting gave a more general definition which still agrees with the classical one in the affine case.
In particular one has:
\begin{equation}
 \GW_i^{[k]}(R) = \begin{array}{cl} \mathrm{KO}_i(R), & k = 0, \\ U_i(R), & k = 1, \\ \mathrm{KSp}_i(R), & k = 2, \\ {}_{-1}\!U_i(R), & k = 3. \end{array}
\end{equation}

\begin{lemma}\label{lem:bass-ft} Suppose that $2 \in R^*$, then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ one has
 \[ \GW_i^{[k]}(R[X, X^{-1}]) \cong \GW_i^{[k]}(R) \oplus \GW_{i-1}^{[k-1]}(R). \] \end{lemma}
\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}

\begin{lemma}\label{lem:summary} Suppose that $F$ is a field of characteristic $\neq 2$, then
$\GW_2^{[3]}(F) = 0$. \end{lemma}
\begin{proof} See~\cite[Lemma~2.2]{FRS12}. \end{proof}

\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}
For a commutative local ring $A$ with the maximal ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$.
Consider the following commutative square of canonical maps.
\[ \xymatrix{
    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]_\mu & \St(\Phi, R)
   } \]
Then there exists an arrow $\mu$ which makes the diagram commute.   
\end{lemma} 
\begin{proof}
 Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
 Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.

@@

The following lemma summarizes facts about $\K_2(\Phi, -)$ in the field case.
\begin{lemma}
 Let $F$ be a field of characteristic $\neq 2$. Then for $\ell \geq 7$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
\end{lemma}
\begin{proof}
 We have defined $\K_3(\rD_\ell, R)$ as 
\end{proof}

\begin{theorem} Suppose $A$ is a local ring of characteristic $\neq 2$, then for $\ell \geq 7$
  the canonical map $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective.
\end{theorem}
\begin{proof}

\end{proof}

\begin{equation*} \xymatrix{
 C(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[r] \ar[d] & \St(\Phi, k[t]) \ar[d] \\
 C(\Phi, R, I) \ar[r]        & \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]& \St(\Phi, R) \ar[r]        & \St(\Phi, k[t, t^{-1}])
}\end{equation*}

@@

%\include{rehmann}
